lab_notebook

### 2018-11-09 lab_notebook.Rmd
- loaded in data (projection and MPA now in .rds not .csv

>>>>

#Loading packages
```{r}
suppressPackageStartupMessages({
  library(tidyverse)
  library(tidyr)
  library(here)
  library(ggplot2)
  library(dplyr)
  library(readxl)
  library(devtools)
  library(plotly)
  library(base)
  library(rio)
})

```

#converting projection csv into rds
no longer need the code because have already used it to create the files
```{r}

#Upside data
#projection_data_csv <- read_csv("data/ProjectionData.csv")

#saveRDS(projection_data_csv, "projection_data.rds")

#WDPA_Nov2018.csv <- read_csv("data/WDPA_Nov2018.csv")

#saveRDS(WDPA_Nov2018.csv, "WDPA_Nov2018.rds")

```

#Load Data
```{r}

#Corbet data: when countries began using RBFs
countries_ITQ <- read_excel("data/Countries_ITQ.xlsx")

#Upside data
projection_data <- readRDS("data/projection_data.rds")

#MPA data
MPA <- readRDS("data/WDPA_Nov2018.rds")

#RAMS
load("data/DBdata-model_fits_included.RData")

number_species <- unique(stock$scientificname)
#341 different species

```

#RAM data wrangling
```{r}

ram <- select(timeseries_values_views, "stockid", "stocklong", "year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

colnames(ram) <- c("stockid", "CommName", "Year", "TBbest", "TCbest", "BdivBmsypref", "UdivUmsypref")

ram_merge <- ram %>%
  unite(Name_Year, "CommName", "Year", sep = "-")

ITQ_projection_year <- ITQ_projection %>%
  unite(Name_Year, "CommName", "Year", sep = "-")

```

Important/Necessary Data
tcbest.data #the best estimate of catch for that stock
tbbest.dat # the best estimate of biomass for that stock
divbpref # B/bmsy
divupref.data # u/umsy

Juliette Notes:

Handy functions for updating data frames:
match()
separate()

Useful Websites:
https://uc-r.github.io/tidyr

#Data Wrangling: Projection and Countries ITQ
```{r}

#seperate out IdOrig column for Projection Data
separate_projection <- projection_data %>% separate(IdOrig, c("agency", "stock", "t0", "tf", "species"))
    ###unsure what the last column actually is, double check

head(separate_projection, 10)

#reunite just the two parts we care about: agency and stock
unite_projection <- separate_projection %>% unite(assess_id_short, agency, stock, sep = "-")

#simplifying Countries ITQ with unique columns to prepare to merge
countries_ITQ_simple <- select(countries_ITQ, "assess_id_short", "year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")

#rename year to be capitalized to merge with projection data
colnames(countries_ITQ_simple) <- c("assess_id_short", "Year", "yearitq", "region_id", "idnumber", "harvest_fb", "itq_now", "iq", "itq", "ivq", "coop", "communityquota", "turf", "individualeffort", "iteq", "totalappliedeffort", "producerorg", "aquaculture", "programstart")

#merging ITQ and Projection
ITQ_projection_merge <- merge(unite_projection,countries_ITQ_simple, by = c("assess_id_short", "Year"))

#cleaning it up
ITQ_projection <- ITQ_projection_merge %>% unite(IdOrig, assess_id_short, t0, tf, species, sep = "-")

```
